\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-28 syntax.tex
additional repling comments
comment

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }\YZreply{
  Changed what? I think Lnkg Add and Sig Add were not changed.
  I still don't see how sealing converts \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}
  and how the latter is now used as the abstracted A.
}\EDJreply{I added the $\goodType{\Gamma}{A}{}$  as you suggested. \\
\cC \{a : \bW sigma ; ..\} is definitionally equal to a sigma type as Compile rule suggested. \\
If you expand the definition, you will see two sigma type. 
You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). \\
This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. And this function's type should be directly the sealing type.}\YZreply{
  My confusion is this: it seems that in Lnkg Add and Sig Add, A could well be the top type and f a value of the top type. In this sense, A seems unspecified.
  Or maybe in the metatheory, it is the programmer's responsibility to find this A?
}\EDJreply{You are absolutely right. In metatheory it is programmer's responsibility to specify the A they want. If they set A to top, they can do that but it will be hard for them to achieve meaningful program. \\
A bit off-topic : this is not the only place that such specification is postponed to the user (in metatheory) another place is in inheritance when specifying upcasting function.}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,
%\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, say ``Ct v'', then this ``Ct v = (Ct p_1 v), (t[sf p_f v][...])'', the f will actually be replaced by p_f; 3. p_f can be used by the user. It doesn't have to interact with other typing rules. }
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

@@

Then any field using "Wsup" and "Wrec", directly relying on the
$\bW\sigma$ in the context (can be spotted from \ruleref{Ind-Term} and
\ruleref{Rec-Constr}), and responsible for exhaustiveness checking will be non-inheritable---in these cases, "Wsup"
can be understood as concrete constructors and "Wrec" are
\textit{exhaustiveness checking}. These fields together with inductive
types are the ones sealing is responsible for hiding. After compilation
of linkage types into existential types, we can easily hide the
\textit{concrete} definition of the inductive type while exposing all
the fields using "Wsup" and "Wrec" like an abstract interface.
Apparently, future fields relying on this abstract interface will have no
problem on inheritance. 
For example, $t_{new}$ above cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor, and also inheritable.
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, like plugin implementation, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear---because I haven't changed any text}

>>>>

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). \\
This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. And this function's type should be directly the sealing type.}\YZreply{
  My confusion is this: it seems that in Lnkg Add and Sig Add, A could well be the top type and f a value of the top type. In this sense, A seems unspecified.
  Or maybe in the metatheory, it is the programmer's responsibility to find this A?
}\EDJreply{You are absolutely right. In metatheory it is programmer's responsibility to specify the A they want. If they set A to top, they can do that but it will be hard for them to achieve meaningful program. \\
Also the `f' is specified together with `A' by the user as well. \\
A bit off-topic : this is not the only place that such specification is postponed to the user (in metatheory) another place is in inheritance when specifying upcasting function.}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,
%\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, say ``Ct v'', then this ``Ct v = (Ct p_1 v), (t[sf p_f v][...])'', the f will actually be replaced by p_f; 3. p_f can be used by the user. It doesn't have to interact with other typing rules. }
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

@@

Then any field using "Wsup" and "Wrec", directly relying on the
$\bW\sigma$ in the context (can be spotted from \ruleref{Ind-Term} and
\ruleref{Rec-Constr}), and responsible for exhaustiveness checking will be non-inheritable---in these cases, "Wsup"
can be understood as concrete constructors and "Wrec" are
\textit{exhaustiveness checking}. These fields together with inductive
types are the ones sealing is responsible for hiding.\YZ{Is sealing really hiding these fields (that use Wsup and Wrec), or is it that the concrete definition of an inductive type is not hidden for these fields so that they can assume knowledge about the inductive type's signature?}
After compilation
of linkage types into existential types, we can easily hide the
\textit{concrete} definition of the inductive type while exposing all
the fields that use "Wsup" and "Wrec" as an abstract interface.
Apparently, future fields relying on this abstract interface will have no
problem on inheritance. 
For example, $t_{new}$ above cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor, and also inheritable.
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, like plugin implementation, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear---because I haven't changed any text}
